Proposal to improve BBC Search through the use of Linked Data

### 2014-05-13 chapter3.2.tex
Almost finished chapter 4.

This works well enough for programmes, but there are areas where
a class-based distinction might not be so clear cut. For example, some articles
on BBC News are accompanied by a video. Is this item textual or a video?
The current search application does not apply a play icon because the
article is classified as textual, as all news story pages are.

>>>>

This works well for programmes, but there are areas where
a class-based distinction might not be so clear cut. For example, some articles
on BBC News are accompanied by a video. Is this item textual or a video?
The current search application does not apply a play icon because the
article is classified as textual, as all news story pages are.

The claim was made that there is limited use in semantically annotating
this metadata as the search application does not \emph{publish} any data
that is not already published in its respective area of the BBC website.
However, given the search system has the primary purpose of bringing
together content across all the BBC (as noted in section~\ref{sec:current-impl}),
relationships are established and those relationships are metadata.
For example, if both a BBC Sport article and a BBC News article mention
the same entity (say, a footballer who has also appeared in the news),
the search application is going to put those two items in the same aggregation
(e.g. search results page) even if just by virtue of keyword matching that
entity's name in both articles.

There is a feature of the current search application where data or metadata
are more directly published and that is the ``Editor's Choice'' feature. In
the next section, the nature of that metadata is explored further.

### 2014-05-13 chapter3.tex
Substantial work on chapter 4. Committing so I don't lose anything.
Some analysis of the results page itself.
Almost finished chapter 4.

\chapter{Analysis}

@@

\input{chapter3.1}

\section{Search Results Page}

The default results page currently returned for a query breaks the individual
results into the zones or categories mentioned in section~\ref{content}. A
navigation menu on the left allows users to drill down into the results just
for that category.

\section{Editor's Choice}

Each and every link promoted within this feature is hand-chosen by editorial
staff and much manual effort is needed to keep promoting new concepts
as they appear and to remove pages as they get superseded. It is hoped
in this proposal we can reduce some of that manual curation through the use
of linked data and demonstrate ways editorial staff can focus on curating
their own linked data such that Editor's Choice could evolve into a more
generalised and automated subsystem. A metadata-driven curation system
could use common patterns in the data to promote orders of magnitude more
top links with a fraction of the current effort.
However, there would be a need to get a list of the known static pages
as they will not appear in the RSS/Atom feeds. Some integration with the
underlying CMS may be necessary or we would have to rely on web crawling
to find these pages.

\section{Search Suggest}

The list of suggestions that might surface in this system are
currently chosen and maintained by hand by editorial staff. If a new
concept breaks into the news (such as a notable person becoming notable
for the first time), then a person must enter that term into the system.
Similarly, if something should not be suggested to users any longer
(perhaps for legal reasons or simply because it is no longer a relevant
concept), then it must be amended or removed manually.

This manual maintenance of the suggestion list also leads to a
disconnect between searchable content and suggested queries that might
appear as users type. There is an onus on editorial staff to ensure
that content will be found when a suggested query is used. It might
serve the website users better to find mechanisms by which to generate
a useful set of suggestions from the corpus of content as it is
indexed. The heterogenous nature of BBC content turns this into
further integration work where different business rules are likely required
to generate suggestions from different types of content.

>>>>

\chapter{Analysis}
\label{analysis}

@@

\input{chapter3.1}
\input{chapter3.2}
\input{chapter3.3}

### 2014-05-13 chapter4.2.tex
Almost finished chapter 4.

\section{Search Results Page}

@@

>>>>

\section{Rich Snippets}

@@

One improvement may be to introduce the rich snippets as described
in section~\ref{enhancing-results}. The work of Haas et
al.\cite{haas2011enhanced} included adding the snippets in the presentation
layer by triggering one of a list of plugins that will alter the
presentation of the data. The indexing process improvements
described in section~\ref{sec:ld-indexing} should provide the
additional structured data to drive a series of rich snippet templates
for different types of content item.

One drawback with creating a template per ``type'' of item is that a
developer has to create each template individually and also add templates
and redeploy the application to add a new type when it emerges.
The RDF model appears to encourage flexibility through
\emph{schemaless} data structures, which could limit the ability to
trigger fixed templates on some types of objects.
